\textsf{Are large language models superhuman chemists?}

### 2024-03-20 src/tex/ms.tex
start working on discussion

\section{Discussion and Conclusions}
Our findings also lay the groundwork for discussions for the chemical education in the future. 
Given that the models outperform the average human in our study, it is clear that we need to rethink the way we teach and examine chemistry.
Critical reasoning is increasingly important and rote solving of problems or memorization of facts is clearly a domain in which \glspl{llm} will continue to outperform humans.

>>>>

\section{Discussion and Conclusions}
One the one hand, our findings show that it is impressive how far we got. Leading models outperform domain experts in chemistry questions on many topics. 
On the other hand, there are still striking limitations. On very relevant topics the answers models provide are wrong. And models are not able to estimate their own limitations.
However, the success in our benchmarks perhaps also reveals more about the limitations about the exams we use to evaluate models---and chemists---than the models themselves.
For instance, while models perform well on many textbook questions, they struggle with questions that require some more reasoning.

Yet, given that the models outperform the average human in our study, it is clear that we need to rethink the way we teach and examine chemistry.
Critical reasoning is increasingly important and rote solving of problems or memorization of facts is clearly a domain in which \glspl{llm} will continue to outperform humans.

Our findings also highlight the nuanced tradeoff between breadth and depth of evaluation frameworks.
